Designing Qusecs Optimally: Quasi-uniform or Self-similar Layered Materials as Recursively Decomposed Solutions of Geometric Constraint Systems

### 2014-12-15 doc/GMP2015/s08_pinnedline.tex
Changed section title. Restated the lemmas and several proofs. Changed figure. Mentioned recombination.

\section{Application: cross-linking microfibrils}

The optimal qusecs DR-plan developed in this paper can be applied to study 
the structure of  cross-linking microfibrils in collagen and cellulose in biology.

Collagen is an important protein material in biological tissues with highly elastic mechanical property. 
Cellulose is the most important constituent of the cell wall of plants (see Figure~\ref{fig:cellulose}). 
Both of these substances consist of a large number microfibrils,
%fibril itself straight?
%Each fibril is attached to some fixed larger organelle/membrane at one spot (typically on the boundary).
%It is additionally 
each of which is cross-linked at 2 places with some two other fibrils, 
where the cross-linking is like an incidence constraint that 
the two crosslinked fibrils can slide with each other (see Figure~\ref{fig:cross-linking}(a). ).

@@

\begin{figure}[hbtp]
\centering
\includegraphics[width=0.5\linewidth]{img/AFM_Innventia_nanocellulose}
\caption{Fibrils of carboxymethylated nanocellulose adsorbed on a silica surface. \cite{xxx}}
\label{fig:cellulose}
\end{figure}

@@

The cross-linking of microfibrils can be modeled using 2-dimensional pinned line incidence constraint system.

%TODO system? problem?
\begin{definition} [2-Dimensional Pinned Line Incidence Graph] \label{prob:pinned_subspace}
A simple graph $G=(V,E)$ is a 2-dimensional pinned line incidence graph, 
if there is  a  set $X$ of $|E|$ pins with fixed positions in $\mathbb{R}^2$.
such that 
 every edge $e \in E$ corresponds to a pin $x \in X$ where $e$ is constrained to lie on a line passing through $x$.
%There exists a set $X$ of $|E|$ pins fixed in $\mathbb{R}^2$, such that each edge $e_i$

@@

In the case of microfibril cross-linking, each fibril is 
attached to some fixed larger organelle/membrane at one spot, 
so it can be modeled as an edge/line segment incident at a pin in $X$. 
%For cross-linking density 2, 
%i.e.\ each fibril has two cross-linkings with other fibrils, 
The cross-linkings can be modeled as vertices in $V$.

\begin{figure}
\centering
\begin{subfigure}{.5\linewidth}
  \centering
  \includegraphics[width=\linewidth]{img/crosslink}
  \caption{}
  \label{fig:sub1}
\end{subfigure}%
\begin{subfigure}{.5\linewidth}
  \centering
  \includegraphics[width=.8\linewidth]{img/teq1}
  \caption{}
  \label{fig:sub2}
\end{subfigure}
\caption{(a) Cross-linking of microfibrils~\cite{xxx}. (b) A pinned line incidence graph.}
\label{fig:cross-linking}
\end{figure}

As an example, Figure~\ref{fig:cross-linking}, 
where the grey ovals stand for pins/attachments of fibrils and the black dots stand for vertices/cross-linkings.
There are 5 edges/fibrils,  and 10 vertices/cross-linkings in the graph.

@@

In this section, we will adapt the results in Section~\ref{xxx}
to give the Optimal DR-plan for 2-dimensional pinned line incidence graphs.
%The 2-dimensional pinned line incidence graphs and their DR-plans have 
Note the following differences from the bar-joint graphs:

@@

\item For pinned line incidence graphs, all vertex weights are $2$, all edge weights are $1$, 
and the constant $k = 0$ \cite{xxxx}. 
%In other words, a pinned line incidence graph is well-constrained if $2|V| = |E|$ and $2|V'| \le |E'|$ for all induced non-trivial subgraphs $S=(V',E') \subseteq G$.

\item 
\todo{Trivial graphs (must be overconstrained in the original definition) does not exist??? }\
\todo{Both a single vertex and a single edge are underconstrained}
\begin{itemize}

\item For  pinned line incidence graphs:
no trivial motion exists since the pins have fixed locations.

\item 
\todo{We just define the trivial graph/DR-plan leaf for 2-dimensional pinned line incidence graphs to be a single vertex.  }

\item \todo{A single edge can be a node of the DR-plan}

@@

\item 
Notice that for pinned line incidence graphs, 
since the pins in $X$ have fixed positions on the plane, 
a well-constrained vertex-maximal proper subgraphs can be disconnected.\\
Without loss of generality, 
we slightly modify the requirement of DR-plan for pinned line incidence graphs
such that only connected subgraphs can be considered as a node of the DR-plan.

With the above modification, 
it is not hard to adapt Theorem~\ref{t1} %, the optimal DR-plan for 2-dimensional bar-joint graphs,
to show the structure of optimal DR-plan for 2-dimensional pinned line incidence graphs.

\begin{corollary}
Given a well-constrained 2-dimensional pinned line incidence graph, for node $C$ in $OptimalDRP(G)$ and the children of $C$ in $CompleteDRP(C)$ labeled as $C_1,\ldots,C_N$
\begin{enumerate}
    \item if $C_i \cap C_j$ is trivial then all $C_1,\ldots,C_N$ are children of $C$ in $OptimalDRP(G)$
    \item if $C_i \cap C_j$ is well-constrained then any two out of $C_1,\ldots,C_N$ will be the only children of $C$ in $OptimalDRP(G)$.
\end{enumerate}
\label{cor:pinned}
\end{corollary}

\todo{All Lemmas before Lemma 8 are proved with respect to general constraint systems,
and they go through for 2-dimensional pinned line incidence as well. }
Now we  show that Lemma 8 also holds for 2-dimensional pinned line incidence graphs.

\begin{proof}[Proof of Lemma~\ref{wc-l3} for 2D pinned line incidence graphs]
We use the same notations as in the proof of Lemma~\ref{wc-c1} in Section~\ref{xxx}.
\begin{itemize}
    \item 4 cases: $C_k$ cannot be $Idc(C,R_i\cup R_j)$, $Idc(C,R'_i\cup R_j)$, $Idc(C,R_i\cup R'_j)$, or $Idc(C,R'_i\cup R'_j)$ because these are all disconnected (Corollary~\ref{wc-c1}) and by our modified requirement of DR-plan nodes.

%    \item 1 case: $C_k=Idc(C,R'_i\cup R'_j\cup D_{i,j})$ is not possible. Since $C_k\cup C_i = Idc(C,R'_i\cup R_j\cup D_{i,j})\neq C$ we have from Lemma \ref{wc-l2} that $C_k\cup C_i$ cannot be well-constrained. We also know it cannot be trivial because it contains well-constrained subgraphs. This means it must be under-constrained. From Lemma \ref{uc-l1}, we know that $C_k\cap C_i=Idc(C,R'_j\cup D_{i,j})$ must then be trivial. This is impossible because $D_{i,j}$ is well-constrained, thereby contradicting the assumption that $C_k$ is well-constrained.
%
%    \item 1 case: \todo{Uses 2D requirement:} $C_k=Idc(C,R'_i\cup R'_j\cup D'_{i,j})$ is not possible. The union with $C_i$ (or $C_j$) is not equal to $C$. Therefore, the union must be under-constrained which means the intersection must be trivial (a single node). However, $C_k\cap C_i=Idc(C,R'_j\cup D'_{i,j})$ and since $R'_j$ and $D'_{i,j}$ are not empty sets, it cannot be trivial making a contradiction.
%
%    \item 2 cases: \todo{Uses 2D requirement:} $C_k=Idc(C,R'_i\cup R_j\cup D'_{i,j})$ and $C_k=Idc(C,R_i\cup R'_j\cup D'_{i,j})$ are not possible. The proof mirrors the previous case, except you must choose $C_i$ and $C_j$, respectively, here.
\end{itemize}

\todo{All other cases are similar to the original proof.}

@@

Given Lemma~\ref{wc-l3}, Lemma~\ref{uc-l2}, Theorem~\ref{uc-t1} and \ref{wc-t1} also apply to  2-dimensional pinned line incidence graphs,
proving Corollary~\ref{cor:pinned}.

Therefore, we can analyze microfibril cross-linkings by finding the optimal DR-plan for  2-dimensional pinned line incidence graphs in the same way as for 2-dimensional bar-joint graphs.

>>>>

\section{Application: finding optimal DR-plans and realizations for cross-linking microfibrils }

The optimal qusecs DR-plan can also be applied to analyze and solve
the structure of  cross-linking microfibrils in collagen and cellulose in biology,
by modeling these structures as {\em pinned line incidence systems}.

{\em Collagen} is an important protein material in biological tissues with highly elastic mechanical property. 
{\em Cellulose} is the most important constituent of the cell wall of plants (see Figure~\ref{fig:cellulose}). 
Both of these substances consist of a large number {\em microfibrils},
%fibril itself straight?
%Each fibril is attached to some fixed larger organelle/membrane at one spot (typically on the boundary).
%It is additionally 
each of which is cross-linked at 2 places with some two other fibrils, 
where the {\em  cross-linking} is like an incidence constraint that 
the two crosslinked fibrils can slide with each other  \cite{xxx} (see Figure~\ref{fig:crosslink}).

@@

\begin{figure}
\centering

\begin{subfigure}{.49\linewidth}
  \centering
  \includegraphics[width=.8\linewidth]{img/AFM_Innventia_nanocellulose}
  \caption{}
  \label{fig:cellulose}
\end{subfigure}
\begin{subfigure}{.49\linewidth}
  \centering
  \includegraphics[width=\linewidth]{img/crosslink}
  \caption{}
  \label{fig:crosslink}
\end{subfigure}%
\caption{(a) Microfibrils of carboxymethylated nanocellulose adsorbed on a silica surface~\cite{xxx}. (b) Cross-linking of cellulose microfibrils~\cite{xxx}.} 
\end{figure}

@@

The cross-linking  microfibrils can be modeled as a 2-dimensional pinned line incidence constraint system, 
where incidence constraints are used instead of distance constraints.

\begin{definition} %[2-Dimensional Pinned Line Incidence Graph] \label{prob:pinned_subspace}
A  graph $G=(V,E, w_V, w_E)$ is a \textbf{2-dimensional pinned line incidence graph}, 
if  $w_V(v) = 2, w_E(e) = 1$ for all $v \in V, e \in E$, and
there is  a  set $X$ of $|E|$ \textbf{pins} with fixed positions in $\mathbb{R}^2$,
such that  %every edge $e \in E$ corresponds to a pin $x \in X$ where 
for each edge $e \in E$, there is a uniquely corresponding pin $x \in X$,
such that $e$ is constrained to lie on a line passing through $x$.
%There exists a set $X$ of $|E|$ pins fixed in $\mathbb{R}^2$, such that each edge $e_i$

@@

\begin{remark}
For 2-dimensional pinned line incidence graphs, 
the constant $k$ used in the definition of independence and rigidity is $0$  \cite{xxx} (see Definition~\ref{xxx}--\ref{xxx}).
\end{remark}

In the case of microfibril cross-linking, each fibril is 
attached to some fixed larger organelle/membrane at one spot.
Consequently, each fibril can be modeled as an edge of the graph, 
with the attachment being the corresponding pin in $X$. 
The two cross-linkings on the fibril are modeled as the two vertices in $V$ defining the edge. 
%so it can be modeled as an edge/line segment incident at a pin in $X$. 
%For cross-linking density 2, 
%i.e.\ each fibril has two cross-linkings with other fibrils, 
%The cross-linkings can be modeled as vertices in $V$.

Figure~\ref{fig:pinned_line} shows an example of a 2-dimensional pinned line incidence graph, 
where the grey ovals stand for pins representing attachments of fibrils, 
and the vertices $a_1,a_2,\ldots, d_3$ represent cross-linkings.
% and the black dots stand for vertices/cross-linkings.
%There are  and 10 vertices/cross-linkings in the graph.
The graph is well-constrained, with 12 vertices and 24 edges/pins.

\begin{figure}
  \centering
  \includegraphics[width=.9\linewidth]{img/pinned}
\caption{ A well-constrained pinned line incidence graph.}
\label{fig:pinned_line}
\end{figure}

@@

In this section, we will adapt the results in Section~\ref{dr}
to give the Optimal DR-plan for 2-dimensional pinned line incidence graphs.
First, we note the following differences of pinned line incidence graphs from the bar-joint graphs.

@@

\item For pinned line incidence graphs, 
since the pins in $X$ have fixed positions on the plane, 
o trivial motion exists, therefore {\em no trivial over-constrained graphs exist} (the smallest over-constrained graph has $6$ vertices).\\
In particular, note that both a single vertex and a single edge are under-constrained graphs.

%\todo{Over-constrained trivial subgraphs does not exist??? }\
%\todo{Both a single vertex and a single edge are underconstrained}
%\begin{itemize}
%%\item For  pinned line incidence graphs:
%%no trivial motion exists since the pins have fixed locations. 
%\item 
%\todo{We just define the %trivial graph/
%DR-plan leaves for 2-dimensional pinned line incidence graphs to be single vertices...  }
%\item \todo{A single edge can be a node of the DR-plan}
%\end{itemize}

\item 
For pinned line incidence graphs, 
since the pins in $X$ have fixed positions on the plane, 
{\em a well-constrained vertex-maximal proper subgraph can be disconnected}, 
being the disjoint union of two or more well-constrained subgraphs. \\
%Without loss of generality, 
%we slightly modify the requirement of DR-plan for pinned line incidence graphs
%such that only connected subgraphs can be considered as a node of the DR-plan.

@@

We make  a few corresponding modifications to the definition of the DR-plan:

%\begin{itemize}
%\item For any $C$, its $N$ children, $C_1, \ldots, C_N$, are {\em edges} or {\em connected} well-constrained vertex-maximal proper subgraphs of that node $C$.
%\item A node containing a single edge is a leaf.
%%\item 
%%\todo{We just define the %trivial graph/
%%DR-plan leaves for 2-dimensional pinned line incidence graphs to be single vertices...  }
%%\item \todo{A single edge can be a node of the DR-plan}
%%\item only connected subgraphs can be considered as a node of the DR-plan.
%\end{itemize}

\begin{definition}

 The \textbf{DR-plan} of  a 2-dimensional pinned line incidence graph $G$ is Definition~\ref{def:drp} with  modified rules number 2 and 4:
%    The \textbf{decomposition-recombination (DR-) plan} of  a 2-dimensional pinned line incidence graph $G$, $DRP(G)$, is  a tree that has the following properties:
    \begin{enumerate}
        %\item The root of the tree `contains' $G$.
        \item[2] For any node $C$, each of its children, $C_1,\ldots,C_N$, is either an edge not contained in any well-constrained proper subgraph of $C$, or a {\em connected} well-constrained vertex-maximal proper subgraph of  $C$.
        %\item The vertex set of $\bigcup_{i=1}^N{C_i}$ is the vertex set of $C$.
        \item[4] A node containing a single edge is a leaf.
    \end{enumerate}
\end{definition}

With the above modification, 
we now adapt Theorem~\ref{t1} %, the optimal DR-plan for 2-dimensional bar-joint graphs,
for the optimal DR-plan for 2-dimensional pinned line incidence graphs.

\begin{corollary}
Given a well-constrained 2-dimensional pinned line incidence graph, for node $C$ in $OptimalDRP(G)$ and the children of $C$ in $CompleteDRP(C)$ labeled as $C_1,\ldots,C_N$
\begin{enumerate}
    \item if $C_i \cap C_j$ is a single vertex then all $C_1,\ldots,C_N$ are children of $C$ in $OptimalDRP(G)$
    \item if $C_i \cap C_j$ is well-constrained then any two out of $C_1,\ldots,C_N$ will be the only children of $C$ in $OptimalDRP(G)$.
\end{enumerate}
\label{cor:pinned}
\end{corollary}

The following lemma serves a similar function to Lemma~\ref{t-l1}--\ref{iuc-l1} in Section~\ref{sec:union_intersection} 
%Using similar counting-based argument, %  to Lemma~\ref{t-l1}--\ref{iuc-l1} in Section~\ref{sec:union_intersection}, 
and can be proved using a similar counting based argument.

\begin{lemma}
\label{lem:pinned_union_intersection}
Let $F_i$ and $F_j$ to be subgraphs of the same well-constrained graph $F$, 
where each of them can be either  a single edge or a connected well-constrained subgraph. 
There are only two possible cases: 
\begin{itemize}
\item At least one of $F_i$, $F_j$ is an edge, if and only if $F_i \cup F_j$ is under-constrained, if and only if $F_i \cap F_j$ is a vertex. 
\item Both $F_i$ and $F_j$ are well-constrained, if and only if $F_i \cup F_j$ is well-constrained, if and only if $F_i \cap F_j$ is well-constrained. 
\end{itemize}

%The following table summarizes all bijections: 
%\setlength{\tabcolsep}{3pt}
%{\small
%\begin{center}
%\begin{tabular}{|p{2.8cm}|c|p{2.3cm}|}
%\hline
%\textbf{Property of $F_i,F_j$} & \textbf{$F_i\cup F_j$} & \centering \textbf{$F_i\cap F_j$}  \tabularnewline \hline
% \centering--- &  \sout{over-constrained}          &  \centering --- \tabularnewline \hline
%at least one of $F_i,F_j$ is an edge & under-constrained       &  \centering a vertex (under-constrained)  \tabularnewline \hline
%both $F_i$ and $F_j$ are well-constrained & well-constrained        &  \centering well-constrained  \tabularnewline \hline
% \centering --- & ---                     &  \centering \sout{under-constrained} \tabularnewline \hline
%\end{tabular}
%\end{center}
%}
%\setlength{\tabcolsep}{6pt}

\end{lemma}

%The proof of Lemma~\ref{lem:pinned_union_intersection} is similar to the proofs of Lemma~\ref{t-l1}--\ref{iuc-l1}.

%\begin{lemma}
%Let $F_j$ and $F_j$ be well-constrained subgraphs of the same well-constrained graph $F$. 
%Both $F_i \cup F_j$ and $F_i \cap F_j$ can only be well-constrained.
%\end{lemma}
%
%\begin{proof}
%\begin{enumerate}
%\item Obviously $F_i \cup F_j$ cannot be over-constrained since it is a subgraph of well-constrained graph $F$.
%\item $F_i \cup F_j$ cannot be under-constrained, otherwise $F_i \cap F_j$ would be over-constrained while there are no trivial over-constrained graphs. 
%\item The only remaining case is that $F_i \cup F_j$ is well-constrained, which is true if and only if $F_i \cap F_j$ is well-constrained.
%\end{enumerate}
%\end{proof}

Proofs of Lemma~\ref{wc-l2} and \ref{wc-c1} straightforwardly extend to 2-dimensional pinned line incidence graphs 
given Lemma~\ref{lem:pinned_union_intersection} and the modified definition of DR-plan.
Now we  show that Lemma~\ref{wc-l3} also holds.

\begin{proof}[Proof of Lemma~\ref{wc-l3} for 2D pinned line incidence graphs]
We use the same notations as in the original proof of Lemma~\ref{wc-l3} in Section~\ref{sec:infer_parent}.

First notice that since $C_i \cup C_j$ is well-constrained, by Lemma~\ref{lem:pinned_union_intersection}, 
both $C_i$ and $C_j$ are connected well-constrained vertex-maximal proper subgraphs of  $C$.
Since $C_j \cup C_j = C$, there are no edges in $C$ that is not contained in a well-constrained subgraph, so $C$ does not have any single-edge child node, and $C_k$ is a connected well-constrained vertex-maximal proper subgraph of  $C$.

Then we analyze all the possible cases for $C_k$.
\begin{itemize}
%    \item 4 cases: $C_k$ cannot be $Idc(C,R_i\cup R_j)$, $Idc(C,R'_i\cup R_j)$, $Idc(C,R_i\cup R'_j)$, or $Idc(C,R'_i\cup R'_j)$ because these are all disconnected (Corollary~\ref{wc-c1}) and by our modified requirement of DR-plan nodes.
    \item 1 case: $C_k=Idc(C,R'_i\cup R'_j\cup D_{i,j})$ is not possible. Since $C_k\cup C_i = Idc(C,R'_i\cup R_j\cup D_{i,j})\neq C$ we have from Lemma \ref{wc-l2} that $C_k\cup C_i$ cannot be well-constrained. 
    By Lemma~\ref{lem:pinned_union_intersection}, it must be under-constrained, 
    so one of $C_i$ and $C_k$ must be an edge, contradicting the assumption that both $C_i$ and $C_k$ are well-constrained.
%    We also know it cannot be trivial because it contains well-constrained subgraphs. This means it must be under-constrained. From Lemma \ref{uc-l1}, we know that $C_k\cap C_i=Idc(C,R'_j\cup D_{i,j})$ must then be trivial. This is impossible because $D_{i,j}$ is well-constrained, thereby contradicting the assumption that $C_k$ is well-constrained.

    \item 1 case: $C_k=Idc(C,R'_i\cup R'_j\cup D'_{i,j})$ is not possible. The proof is similar to the previous case.  
%    union with $C_i$ (or $C_j$) is not equal to $C$. Therefore, the union must be under-constrained which means the intersection must be trivial (a single node). However, $C_k\cap C_i=Idc(C,R'_j\cup D'_{i,j})$ and since $R'_j$ and $D'_{i,j}$ are not empty sets, it cannot be trivial making a contradiction.

    \item 2 cases: $C_k=Idc(C,R'_i\cup R_j\cup D'_{i,j})$ and $C_k=Idc(C,R_i\cup R'_j\cup D'_{i,j})$ are not possible. 
    The proof is similar to the previous case.  
    %The proof mirrors the previous case, except you must choose $C_i$ and $C_j$, respectively, here.
\end{itemize}

All the remaining cases are similar to the original proof.

@@

The following lemma serves as Lemma~\ref{uc-l2} for pinned line incidence and can be proved similarly.
\begin{lemma}
\label{lem:vertex_intersection}
If $C_i\cap C_j$ is a single vertex, then $\forall k: C_i\cap C_k$ is a single vertex.
\end{lemma}

Given Lemma~\ref{wc-l3} and Lemma~\ref{lem:vertex_intersection}, 
it is straightforward to adapt the proof of Theorem~\ref{uc-t1} and \ref{wc-t1} 
to  2-dimensional pinned line incidence graphs,
thus proving Corollary~\ref{cor:pinned}. 
Consequently, we can efficiently find the optimal DR-plan for 2-dimensional pinned line incidence graphs using basically the same algorithm as for 2-dimensional bar-joint graphs.
%we can analyze microfibril cross-linkings by finding the optimal DR-plan for  2-dimensional pinned line incidence graphs in the same way as for 2-dimensional bar-joint graphs.

%TODO ???
The recombination problem for 2-dimensional pinned line incidence systems is trivial. 
Since the pins are given fixed positions in the plane, 
once we get a solution a well-constrained sub-system, 
the solution will automatically be consistent with the remaining of the system.
